% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hongtao Zhang}

\basicInfo{
  \email{hzhang784@wisc.edu} \textperiodcentered\
  \phone{(608)960-6817} \textperiodcentered\
  \linkedin[hongtao]{https://www.linkedin.com/in/hongtao-zhang-358458207/}\textperiodcentered\
  \textbf{Github:} \href{https://github.com/taooceros}{taooceros}
}

\section{\texorpdfstring{\faGraduationCap}{}\ Education}
\datedsubsection{\textbf{University of Wisconsin Madison}}{\textit{Madison, WI}, 12/2024}
\textit{B.S.} in Computer Science, Mathematics, Statistics, Data Science\textperiodcentered\ \textit{L\&S Honors}\\
\textbf{GPA}: 4.0/4.0.
\section{\texorpdfstring{\faUsers}{}\ Experience}
\datedsubsection{\textbf{\href{https://www.flowlauncher.com/}{Flow Launcher} | Github Open Source Project | 1.8k \texorpdfstring{\faStar}{Star}}}{10/2020 -- Present}
\role{C\# (.Net Core)}{Member}
A plugin-driven launcher for Windows that help users to quickly launch apps, explore file/folder, and customizable functionalities with plugins.
\begin{itemize}
  \item Optimized display machamism to prevent freezing when processing large scale of results (10000+).
  \item Redesigned communication protocol with plugins written in other language with \textbf{JSONRPC} Protocol.
  \item Rewrote plugin parallel co-routine model and Revised Asynchronous Event Loop system with Producer/Consumer Model.
  \item Designed and Implemented Extendable Highlight Mapping API transfering Pinyin query match to highlight displayed in Chinese with Range Binary Search to allow Pinyin user to understand the query match.
  \item Refactored UI Component with \textbf{\textit{WPF}} MVVM. Expanded 20+ external API to provide more flexibility to plugin authors.
  \item Organized community activities (Answer Issues/Discussions, Review Pull Requests, Draft Future Routes).
  \item Constructed and Managed the Translation CI/CD with \textit{Crowdin}.
  \item \texorpdfstring{\faStar}{Star} increased from 180 to 1.8k.
\end{itemize}

\datedsubsection{\textbf{\href{https://github.com/taooceros/Flow.Plugin.WindowWalker}{Flow.Plugin.WindowWalker}}}{01/2021 -- Present}
\role{C\# (.Net Core), Maintainer}{}
A Plugin of Flow Launcher to switch between opened windows.
\begin{itemize}
  \item Implemented Quick Window Search to allow customizable query, and allowed user to close specific window by hotkey.
  \item Utilized FuzzySearch API from Flow Launcher to provide better and more integrated search experience to user.
  \item Achieved Localization based on .Net Resources (Resx) file and Improved Performance by 30\%.
  \item Designed CI/CD with \textbf{\textit{Github Action}} (widely used in other plugins).
\end{itemize}

\datedsubsection{\textbf{\href{https://github.com/Flow-Launcher/Flow.Launcher.PluginsManifest}{Flow Launcher PluginsManifest}}}{01/2021 -- Present}
Plugin Management Repository for Flow Launcher
\begin{itemize}
  \item Designed the CI/CD with \textbf{\textit{Github Action}} to auto fetch plugin update information, and review new plugin submission PRs.
  \item Utilized CDN from \href{https://www.jsdelivr.com/}{\textit{jsDelivr}} to optimize network access toward icons of plugins.
\end{itemize}

\datedsubsection{\textbf{\href{https://www.flowlauncher.com/docs/}{Flow Launcher Docs}}}{05/2021 -- Present}
Document Websites for Flow Launcher Based on \href{https://docsify.js.org/#/}{\textit{docsify}}
\begin{itemize}
  \item Revised styles. Wrote tutorial and document, and generated API Reference for .Net plugin development.
\end{itemize}

\datedsubsection{\textbf{\href{https://vmawalk.vercel.app/}{VMAwalk}}}{06/2020 -- 01/2021}
\role{HTML/CSS/JavaScript/C\#}{Individual Project, collaborated with \linkedin[Jeffrey Yu]{https://www.linkedin.com/in/jeffrey-zepeng-yu/} and \linkedin[Peng Qiu]{https://www.linkedin.com/in/peng-qiu-a791a2178/}}
A peer-review platform for teachers and Courses for Vanke Meisha Academy.
\begin{itemize}
  \item Constructed and Managed the \textbf{\textit{MS-SQL}} Database. Utilized \textbf{\textit{Entity Framework Core}} to implement the Data Access Layer.
  \item Implemented the BackEnd Restful API (\textbf{\textit{ASP.Net Core}}) and User Management System Based on \textit{JWT}.
  \item Implemented FrontEnd Pinyin and Acronym Fuzzy Search and Front-Back Communication with \textbf{\textit{JQuery}}
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\texorpdfstring{\faCogs}{}\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Programming Languages}: C, C++, Python, Java, Go, JavaScript, TypeScript, R, Matlab, HTML, CSS, \LaTeX
  \item \textbf{Framework \& Tools}: ASP.NET Core, Blazor, WPF, Sql-Server, Vue.js, React.js, Chakra UI, Qt, Node, Express.js, Django, Flask, Graphene, SQLAlchemy, Web Crawler, Pandas, Jupyter, Axios, JQuery, Nginx, Gunicorn
\end{itemize}



%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
